\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-02 letter.tex
fix typos in sec:main, remove assumption 2 content from res:lobby
add paragraph to letter on R2

Referee's point $\#2$ (``Intuition in the Introduction about political uncertainty''):

@@

>>>>

Referee's point $\#2$ (``Intuition in the Introduction about political uncertainty''): There are several kinds of intuition about political uncertainty, and I struggled a bit to guess which kind was meant. Because I already give some intuition about the effects of political uncertainty on the results, I went with the interpretation that this meant intuition/interpretation about what I mean by political uncertainty itself. I have thus added a few sentences in the fifth paragraph of the introduction to this end. I would be happy to do something different/additional if I have interpreted this suggestion incorrectly.

@@

\vskip.5in
Other changes
\begin{itemize}
	\item I have removed the statement ``and the distribution of $\gamma(e,\theta)$ is weakly increasing in $e$'' from Result 2 because this is the content of Assumption 2 and does not need to be repeated.
\end{itemize}
